---
title: "guns"
author: "Justin Herman"
date: "8/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dangers of data visualization

Visualization allows analysts to convey important knowledge in digestible manners.  However, analysts have to make assumptions all the time in attempting to convey messages.  Sometimes, as an unintended consequnce visualizations can be extremely misleading.  With the horrific events in El Paso and Dayton in the beggining of August, publications are attempting to communicate to audiences via visualizations of these mass shootings.  Mother Jones has a  Given the Horriffic events in Elpaso and [[ nsert here]], I wanted to look at different ways to visualize the data behind mass shooting.  I understand the sensative nature of this topic, and in no way do I intend to undermine the horriffic situation that America has found itself in.  However, I believe it does serve as a pertinent example of understanding how vastly different visualizations can appear, given different assumptions. 

Below 


```{r}
library(tidyverse)
library(dplyr)
library(readxl)
library(knitr)
library(kableExtra)
library(xtable)
library(lubridate)
library(gganimate)
library(cowplot)
library(plotly)
guns <- read.csv("https://raw.githubusercontent.com/justinherman42/Media_Bias_project/master/Guns_Visualizations/csv_files/Mother%20Jones.csv")

```

```{r,echo=F}
### General data Manipulations

## convert Date to Date type
guns <- guns%>% 
    mutate(date=lubridate::mdy(date))

## make prediential name terms
guns$president<- cut(guns$year, 
                   breaks=c(1980,1988,1992,2000,2008,2016,2020), 
                   labels=c("Reagan","BushSr","Clinton","Bushjr","Obama","Trump"))

### Build weights and build numeric column based on weights that normalizes each presidency to 1 term
days_in_office_Trump <- as.numeric(Sys.Date()-as.Date("2017-01-20"))
guns$weights<- 1
guns$weights[guns$president=="Trump"] <- 1/(days_in_office_Trump/(365*4))
guns$weights[guns$president=="Obama"] <- .5
guns$weights[guns$president=="Reagan"] <- .5
guns$weights[guns$president=="Clinton"] <- .5
guns <- guns %>% 
    mutate(total_victims_per_term= total_victims*weights)
#guns <- as.data.frame(guns)

##make other race column inclusive of (-,unclear/other)
guns[,"race"] = toupper(guns[,"race"])
guns$race <- trimws(toupper(as.character(guns$race)))
guns$race[guns$race %in% c("OTHER","-","UNCLEAR",NA) ] <- "OTHER/ UNKOWN"

## Make shorter summary column for plotly graphs
y=1
for (x in guns$summary){
  guns$summarytext[y] <- paste(substr(x,1,75))
   y=y+1
  }

## build df without vegas
minus_lv <- guns %>% 
    filter(injured!=546	)
```



```{r}
## build bar graph with vegas
with_lv <- ggplot(guns,  aes(x=president, y=total_victims)) + 
  geom_bar(stat='identity',fill="steelblue")+
      theme(axis.text.x=element_text(angle=90,hjust=1),
            legend.position="none")+
  ggtitle("With Vegas")+
   labs(x = "", y = "total # victims")

## build bar grpah wtihout vegas
without_lv <- ggplot(minus_lv,  aes(x=president, y=total_victims)) + 
  geom_bar(stat='identity',fill="steelblue")+
      theme(axis.text.x=element_text(angle=90,hjust=1),
            legend.position="none")+
  ggtitle("Without Vegas")+
   labs(x = "", y = "total # victims")

##Normalize per term 
normalized_withlv <- ggplot(guns, aes(x=president, y=total_victims_per_term)) + 
  geom_bar(stat='identity',fill="steelblue")+
      theme(axis.text.x=element_text(angle=90,hjust=1),
            legend.position="none")+
    ggtitle("Per Term With Vegas")+
   labs(x = "", y = "total # victims")

normalized_without_lv <- ggplot(minus_lv,  aes(x=president, y=total_victims_per_term)) + 
  geom_bar(stat='identity',fill="steelblue")+
      theme(axis.text.x=element_text(angle=90,hjust=1),
            legend.position="none")+
    ggtitle("Per Term Without Vegas")+
   labs(x = "", y = "total # victims")


# ggplot(guns, aes(x=president, y=total_victims_per_term)) + 
#   geom_segment(aes(x = 0, y = president, xend = total_victims_per_term, yend = president), color = "grey50")+
#   geom_point()
#   
#       theme(axis.text.x=element_text(angle=90,hjust=1),
#             legend.position="none")+
#     ggtitle("Per Term With Vegas")




## plot both graphs
breakdown_by_president <- plot_grid(with_lv,without_lv,normalized_withlv,normalized_without_lv)
save_plot("Breakdown_by_president.png",breakdown_by_president)
breakdown_by_president

subplot(ggplotly(with_lv),ggplotly(without_lv),ggplotly(normalized_withlv),ggplotly(normalized_without_lv),nrows=2)
```


##timeline plot

```{r}
ggplot(guns,aes(x=date,y=0, col=total_victims, label=total_victims))+
  labs(col="total_victims")+
  theme_classic()+
  geom_hline(yintercept=0, 
                color = "black", size=0.3)


#dislocations <- c(-1,1,-.5)#
bubble_chart <- ggplot(guns,aes(x=date,y=total_victims, col=president, label=total_victims,size=total_victims)) +
  geom_point(stat="identity")+
   theme(axis.line=element_blank()
         ,
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),legend.position="none")+
    #   geom_label(x = as.Date('1990-10-01'), y =400, label = "not working right") +
  annotate("text",x = as.Date('2014-10-01'), y =550, label = "Las Vegas Shooting",arrow=arrow(), color = "red")+
   annotate("segment",x = as.Date('2014-10-01'),xend=as.Date('2017-04-01'), y =550,yend=600,arrow=arrow(), color = "red")
       
ggplotly(bubble_chart)
```




```{r}



## plot by race
a <- ggplot(minus_lv, aes(x=race, y=total_victims,fill="steelblue")) + 
  geom_bar(stat='identity',color="steelblue")+
      theme(axis.text.x=element_text(angle=90,hjust=1),legend.position="none") +
  coord_flip()
ggplotly(a)



## time plot showing victems
d <- ggplot(guns,aes(x=date,y=total_victims, col=president, label=total_victims,size=total_victims, group = 1,text = summarytext)) +
  geom_smooth(method='lm',formula=y~x)+
  geom_point(stat="identity",fill="black")+
   theme(axis.line=element_blank()
         ,axis.title.x=element_blank(),
          axis.title.y=element_blank(),legend.position="none")+
  annotate("text",x = as.Date('2014-10-01'), y =550, label = "Las Vegas Shooting",arrow=arrow(), color = "red")+
   annotate("segment",x = as.Date('2014-10-01'),xend=as.Date('2017-04-01'), y =550,yend=600,arrow=arrow(), color = "red")+
   ggtitle("Mass Shooting by presidency")
  

## time plot showing victems wihtout Vegas
e <- ggplot(minus_lv,aes(x=date,y=total_victims, col=president, label=total_victims,size=total_victims, group = 1,text = summarytext )) +
  geom_smooth(method='lm',formula=y~x)+
  geom_point(stat="identity",fill="black")+
   theme(axis.line=element_blank()
         ,axis.title.x=element_blank(),
          axis.title.y=element_blank(),legend.position="none")+
   ggtitle("Mass Shooting by presidency")



mass_shooting <- subplot(ggplotly(d,tooltip = c('text',"label",'x','president')),ggplotly(e,tooltip = c('text',"label",'x','president'))) %>% 
  layout(annotations = list(
 list(x = 0 , y = 1.05, text = "Including Las Vegas", showarrow = F, xref='paper', yref='paper'),
  list(x = .8 , y = 1.05, text = "Excluding Las Vegas", showarrow = F, xref='paper', yref='paper'))
)
mass_shooting
# ggsave("myplot.pdf")
Sys.setenv("plotly_username"="justinherman42")
Sys.setenv("plotly_api_key"="1MPl8MFGmpgXWhC5m6C7")
api_create(mass_shooting, filename = "Visualizing mass shooting by president")

```



```{r}

## Start to build out Time Series df for GGanimate
guns <- guns %>% 
    arrange(date)

## Below steps build out columns for every combination of Date/Race
allnames <- data.frame(rep(unique(guns$race),35))
build_dates <- rep(unique(guns$year),6)
build_dates <- sort(build_dates)
cart_df <- as.data.frame(cbind(allnames,build_dates))
colnames(cart_df) <- c("race","year")
guns$race<- as.factor(guns$race)

##Join  on Cartesian DF 
aa <- plyr::join(cart_df,guns,type="left", by=c("race","year"))
aa$total_victims[is.na(aa$total_victims)] <- 0
aa <- aa %>% 
    arrange(race,year)

###build out diff visuals
aa2 <- aa %>% 
    group_by(year,race) %>% 
    summarise(yearly_death_per_race=sum(total_victims))
aa2$president<- cut(aa2$year, 
                   breaks=c(1980,1988,1992,2000,2008,2016,2020), 
                   labels=c("Reagan","BushSr","Clinton","Bushjr","Obama","Trump"))



aa2$total_victims <- ave(aa2$yearly_death_per_race, aa2$race, FUN=cumsum)

p<- ggplot(aa2, aes(x=race, y=total_victims)) + 
  geom_bar(stat='identity')+
      theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("Race of Shooter")+
    labs(title="Cumulative Victims by race of shooter up to  {closest_state}") +
    transition_states(year)

animate(p+coord_flip())


p2<- ggplot(aa2, aes(x=race, y=total_victims,fill="steelblue")) + 
  geom_bar(stat='identity')+
      theme(axis.text.x=element_text(angle=90,hjust=1))+
    xlab("Race of Shooter")+
    labs(title="Cumulative Victims by race of shooter up to  {closest_state}") +
    transition_states(year)

animate(p2+coord_flip(), renderer = gifski_renderer(loop = F))




aa3 <- aa %>%
    filter(! president%in% c("Trump","Obama")) %>% 
    group_by(year,race) %>% 
    summarise(yearly_death_per_race=sum(total_victims))
aa3$total_victims <- ave(aa3$yearly_death_per_race, aa3$race, FUN=cumsum)
```



```{r}
## Expand DF to Build out a DF with every combination of President/race/year
allnames <- data.frame(rep(unique(guns$race),35*6))
build_dates <- rep(unique(guns$year),6*6)
build_dates <- sort(build_dates)
build_presidents <- rep(unique(guns$president),6)
build_presidents <- sort(build_presidents)
cart_df <- as.data.frame(cbind(allnames,build_dates,build_presidents))
colnames(cart_df) <- c("race","year","president")
guns$race<- as.factor(guns$race)

## Join on cartesian DF 
aa <- plyr::join(cart_df,guns,type="left", by=c("race","year","president"))
aa$total_victims[is.na(aa$total_victims)] <- 0
aa <- aa %>% 
    arrange(race,year,president)

###build out diff visuals
aa2 <- aa %>% 
    group_by(year,race,president) %>% 
    summarise(yearly_death_per_race=sum(total_victims))
#aa4 <- aa2 %>% group_by(year,race,president) %>% 
#    summarise(sum_sum_race=cumsum(yearly_death_per_race),yearly_death_per_race)
aa2$total_victims <- ave(aa2$yearly_death_per_race, aa2$race,aa2$president, FUN=cumsum)

## build animation    
p<- ggplot(aa2, aes(x=race, y=total_victims,fill=race)) + 
  geom_bar(stat='identity')+
      theme(axis.text.x=element_text(angle=90,hjust=1))+
    facet_wrap(~president)+
    xlab("Race of Shooter")+
    labs(title="Cumulative Victims by race of shooter up to  {closest_state}") +
    transition_states(year)

## display/save animation
animate(p, renderer = gifski_renderer(loop = F))
anim_save("with_vegas.gif", animation = last_animation())
```



```{r}
## Repeat step above this time without Mandalay Bay
guns <- guns %>% 
    filter(injured!=546	)
allnames <- data.frame(rep(unique(guns$race),35*6))
build_dates <- rep(unique(guns$year),6*6)
build_dates <- sort(build_dates)
build_presidents <- rep(unique(guns$president),6)
build_presidents <- sort(build_presidents)
cart_df <- as.data.frame(cbind(allnames,build_dates,build_presidents))
colnames(cart_df) <- c("race","year","president")

## build our df
guns$race<- as.factor(guns$race)

##cartesian join 
aa <- plyr::join(cart_df,guns,type="left", by=c("race","year","president"))
aa$total_victims[is.na(aa$total_victims)] <- 0
aa <- aa %>% 
    arrange(race,year,president)

###build out diff visuals
aa2 <- aa %>% 
    group_by(year,race,president) %>% 
    summarise(yearly_death_per_race=sum(total_victims))
aa2$total_victims <- ave(aa2$yearly_death_per_race, aa2$race,aa2$president, FUN=cumsum)

p<- ggplot(aa2, aes(x=race, y=total_victims,fill=race)) + 
  geom_bar(stat='identity')+
      theme(axis.text.x=element_text(angle=90,hjust=1))+
    facet_wrap(~president)+
    xlab("Race of Shooter")+
    labs(title="Cumulative Victims by race of shooter up to  {closest_state} Excluding Madalay Bay event") +
    transition_states(year)

animate(p, renderer = gifski_renderer(loop = F))
anim_save("without_vegas.gif", animation = last_animation())
```


## test for change in mean between Obama and Trump by quarter

```{r}
modern_day <- guns %>% 
  filter(president%in%c("Trump","Obama"))


od2 <- modern_day %>% 
  group_by(quarter(modern_day$date, with_year = TRUE)) %>% 
  summarise(injuries=sum(total_victims))
quarter(modern_day$date, with_year = TRUE)
```

